Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Reference Scantegrity ballot auditing in its description

% don't number sections
%\setcounter{secnumdepth}{0}

@@

@@

Additionally, during the voting process, a voter can ask a poll worker for an second ``audit''
ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
revealed, and the ballot is marked as an audit ballot. An audit ballot is scanned, but the voter is
allowed to keep the ballot for later verification.

>>>>

@@

After these tables have been generated, the election authority must \term{commit} to their contents
so that any change from this point forward is impossible or detectable.

It is at this point that the election authority audits a selection of the ballots; this is discussed
further in our analysis.

@@

Additionally, during the voting process, a voter can ask a poll worker for an second ``audit''
ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
revealed, and the ballot is marked as an audit ballot. An audit ballot is scanned, but the voter is
allowed to keep the ballot for later verification. This verification process is described and
discussed in our analysis.
